#Linear Regression To Calculate Profits For Food Truck
```{r eval = F}
require(devtools)
install_github('rCharts', 'ramnathv')
rCharts::open_notebook()
```

Linear Regression Approach To Predict Profits To a Food Truck

We implement linear regression with one variable to predict profits for a food truck. Suppose you are the CEO of a restaurant franchise and are considering different cities for opening a new outlet. The chain already has trucks in various cities and you have data for profits and populations from the cities.

We would like to use this data to help you select which city to expand to next.

##Input Dataset:

The file ex1data1.txt contains the dataset for our linear regression problem. The first column is the population of a city and the second column is the profit of a food truck in that city. A negative value for profit indicates a loss.
```{r eval = F}
require(devtools)
install_github('rCharts', 'ramnathv')
rCharts::open_notebook()
```
```{r echo = T, message = F, cache = F}
library(googleVis)
op <- options(gvis.plot.tag='chart')
require(rCharts)
options(RCHART_WIDTH = 300, RCHART_HEIGHT = 200)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = F)
```
<style>.rChart {width: 600px; height: 400px;}</style>

## Linear Regression Using rChart

```{r, message=F, warning=F}
library(googleVis)
library(rCharts)
library(ggplot2)
```

```{r, echo=FALSE, eval=TRUE}
truckData<-read.csv('ex1data1.txt',header=FALSE)
colnames(truckData)<-c('Population','Profit')
dat = fortify(lm(Population~Profit, data = truckData))
names(dat) = gsub('\\.', '_', names(dat))
```

```{r gvisScatterChart, results='asis'}
Scatter1 <- gvisScatterChart(truckData,options=list(legend="none",title="Food Truck", vAxis="{title:'Profit in $10,000s'}",hAxis="{title:'Population of City in 10,000s'}", width=300, height=300))
plot(Scatter1)
```


```{r chart2, results='asis'}
p1 <- rPlot(Population ~ Profit, data = dat, type='point')
p1$layer(y = '_fitted', copy_layer = T, type = 'line',
  color = list(const = 'red'),
  tooltip = "function(item){return item._fitted}")
p1$print('chart2')
```


##Regression Analysis Using Gradient Descent:


